Mathematical Language Processing \\ Project

### 2014-06-20 paper.tex
fix final todo

\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{arrows,backgrounds,positioning}
\usepackage{todonotes}

@@

To build such a system, a labeled text corpus that annotates identifiers and
their definition is desirable. At the project start, such a corpus was not
available.
We calculate the probablities for correct identifier definition tuples based
on part-of-speech (POS) tagged based distance metrics.
\todo{rewrite sentences to make it process more clear}
 The motivation for our
choice is that readers usually extract identifier definitions from context
that is given by the surrounding text. In combination with the Stratosphere
system \cite{Alexandrov2010} that is capable of scalable data processing, we
rapidly generate a large amount of definition relation candidates with only
minimal implementation overhead for the parallelization.

@@

\paragraph{Observations.} We observed some poorly ranked relations. For
example, in the fragment \texttt{`where $\phi$( $r_{i}$ ) is the electrostatic
potential'}, the distance $\Delta(\phi, \mathsf{electrostatic\:potential} ) = 6$. This is due
to counting brackets and function arguments as words. Also wrongly tagged
words like `Hamiltonian' as an adjective leads to false negatives.

>>>>

\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{arrows,backgrounds,positioning}

@@

To build such a system, a labeled text corpus that annotates identifiers and
their definition is desirable. At the project start, such a corpus was not
available.
Consequently we had to start manual investigation of individual articles.
Our first observation was many identifier definitions use a fixed string pattern
to explain the definition to the reader. Furhtermore most
definitions are usually very close to the occurence of the identifier.
Thus we calculate the probablities for correct identifier definition tuples based
on part-of-speech (POS) tagged based distance metrics.
This correlates to the experience that readers usually extract identifier definitions from context
that is given by the surrounding text. In combination with the Stratosphere
system \cite{Alexandrov2010} that is capable of scalable data processing, we
rapidly generate a large amount of definition relation candidates with only
minimal implementation overhead for the parallelization.

@@

\paragraph{Observations.} We observed some poorly ranked relations. For
example, in the fragment \texttt{`where $\phi$( $r_{i}$ ) is the electrostatic
potential'}, the distance is %\newline
$\Delta(\phi, \mathsf{electrostatic\:potential} ) = 6$. This is due
to counting brackets and function arguments as words. Also wrongly tagged
words like `Hamiltonian' as an adjective leads to false negatives.
